The Dynamics of Anthropomorphism in Human-Robot Interaction

### 2014-04-02 paper.tex
started working on summary of section 3 (first 2)

Summing it up, anthropomorphism is a commonly discussed and
studied trait of human-robot interaction; however its current understanding seems to be stuck in a twofold consideration. Mostly, only two key factors are recognized: the
characteristics of \textbf{1) the robot's design} (degree of human-likeness) and
the psychological determinants in \textbf{2) the human user} (see
\cite{epley_seeing_2007}). A lot of research has shown that both these factors can
promote or hinder anthropomorphism.
However, anthropomorphism is a complex process and we think that the current understanding of it does neither seem to fully take into account the wide range of phenomena that it encompasses, nor the multiplicity of factors which determine it.
This shortcoming and conflict in the understanding of anthropomorphism in HRI has already been denoted by others but we would like to take a first step towards moving forward in this dilemma, and encourage an open dialogue to solve this.

Through applying an understanding that anthropomorphism represents a specific type of \textit{experience} that arises in the
\textit{interaction} between a set of user expectations and external reality, 
%(see Figure~\ref{fig:anthropomorphism_and_interaction})
we propose that
anthropomorphism is a multi-layered phenomenon which arises in different levels \citep{persson_anthropomorphism_2000}, and which is likely to evolve with continued interaction.
%we suggest to understand anthropomorphism as a \emph{dynamic},
%\emph{context-dependent} process. To this end, we apply Persson \textit{et
%al.}'s six levels on anthropomorphism to HRI and introduce three
%\emph{interaction phases}. These interaction phases of anthropomorphism reflect
%also the results of a long-term study that we conducted in a real human
%environment and provide an account of the so-called \textit{novelty effect}.

To this end, and in respect of our research hypotheses, we make the following two suggestions:

First, we propose to include two more main factors as determinants of anthropomorphism (besides the robot's design, and the human user's characteristics). Namely, these factors are \textbf{3) the context of use} (situation) and the fact of getting used to a system the more and longer one interacts with it, thus becoming familiar with the system over \textbf{4) time}.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{factors}
    \caption{Anthropomorphism is a multi-factor phenomenon. How far people tend to anthropomorphize a robot is determined by four main factors: the design of the robot $(R)$, the personal characteristics of the human user $(H)$, the situation and context in which the interaction occurs $(C)$, and the amount of time (repeated interaction) that the user spends to familiarize herself with the robot $(t)$.}
    \label{factors}
\end{figure}

>>>>

Summing it up, anthropomorphism is a commonly discussed and
studied trait of human-robot interaction; however its current understanding seems to be stuck.
More concretely, when seeking to understand why anthropomorphism in an interaction between a human and a non-human artifact happens, most attention is given to the artifact and/or to the human. We agree that these two are the essential `players' of anthropomorphism (see Figure \ref{fig:anthropofig}). Indeed and, as outlined before, research has shown that both the human and the artifact are not only the two players of anthropomorphism but also the two main `factors' that can promote or hinder anthropomorphism.

However, we think that this is not the full story. When agreeing to understand anthropomorphism as a specific type of \textit{experience} that arises in an
\textit{interaction} between a set of user expectations and the external reality, 
%(see Figure~\ref{fig:anthropomorphism_and_interaction})
it becomes clear that this interaction happens in a specific context, with a specific history. We think that the context and the history of the interaction (in Figure \ref{fig:factors} denoted as \textit{time}), are two more factors that determine anthropomorphism.

Consequently, we propose a holistic understanding of anthropomorphism as a phenomenon which is determined by multiple factors:

\item ~the \textbf{characteristics of the robot's design} (degree of anthropomorphic form),
\item ~the \textbf{psychological determinants in the human user} (see
\cite{epley_seeing_2007}),
\item ~the \textbf{characteristics of the context} (situation) in which the interaction occurs, and
\item ~the fact of the user getting \textbf{familiar with the robot over time} (getting used to a system the more and longer one interacts with it)

Further, we propose that
anthropomorphism is a multi-layered phenomenon which arises in different levels \citep{persson_anthropomorphism_2000}, and which is likely to evolve with continued interaction.

%However, anthropomorphism is a complex process and we think that the current understanding of it does neither seem to fully take into account the wide range of phenomena that it encompasses, nor the multiplicity of factors which determine it.
%This shortcoming and conflict in the understanding of anthropomorphism in HRI has already been denoted by others but we would like to take a first step towards moving forward in this dilemma, and encourage an open dialogue to solve this.

%we suggest to understand anthropomorphism as a \emph{dynamic},
%\emph{context-dependent} process. To this end, we apply Persson \textit{et
%al.}'s six levels on anthropomorphism to HRI and introduce three
%\emph{interaction phases}. These interaction phases of anthropomorphism reflect
%also the results of a long-term study that we conducted in a real human
%environment and provide an account of the so-called \textit{novelty effect}.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{factors}
    \caption{Anthropomorphism is a multi-factor phenomenon. How far people tend to anthropomorphize a robot is determined by four main factors: the design of the robot $(R)$, the personal characteristics of the human user $(H)$, the situation and context in which the interaction occurs $(C)$, and the amount of time (repeated interaction) that the user spends to familiarize herself with the robot $(t)$.}
    \label{fig:factors}
\end{figure}
